---
title: "Data_wrangling_1"
author: "Shan Jiang"
date: "9/18/2018"
output: github_document
---

```{r 1, echo=FALSE}
library(tidyverse)
getwd()
```
## the relative path is much better than absolute path
# Import my first CSV(Compiled).
```{r 2}
litters_data = read.csv(file = "./data_import_examples/FAS_litters.csv")
names(litters_data)
litters_data = janitor::clean_names(litters_data)

```
## look at pups data:janitor is used for cleaning the data variable names
```{r 3}
pups_data = read.csv(file = "./data_import_examples/FAS_pups.csv")
pups_data = read.csv(file = "~/Downloads/Data Science/2.data Wrangl/Data_Wrangling/data_import_examples/FAS_pups.csv")
names(pups_data)
pup_data = janitor::clean_names(pups_data)
skimr::skim(pups_data)
```
## skim in r is a quick summary of data
```{r 4}
head(litters_data)
tail(litters_data)
skimr::skim(litters_data)
```
## View button is quite useful, and this function is case sensitive.
```{r 5}
litters_data = read_csv(file = "./data_import_examples/FAS_litters.csv",col_types = "ccddiiii"
)
litters_data
tail(litters_data)
```
## read mlb data excel sheet cannot be read straightforward, coverting is not easy.Use read.excel

To get a subset of the spreadsheet:
```{r 6}
mlb_data = readxl::read_excel(path = "./data_import_examples/mlb11.xlsx")
mlb_subset = readxl::read_excel(path = "./data_import_examples/mlb11.xlsx", 
                                range = "A1:E17")
```
## read the SAS data; **View is case sensitive**
```{r 7}
pulse_data = haven::read_sas("./data_import_examples/public_pulse_data.sas7bdat")
View(pulse_data)
```
the **read_csv** is just a simple one 
while the **read.csv** will list all the rows in the data frame

tibbles for pretty much everything;
